### 2013-08-21 Tex/chapters/results.tex
kleiner Verbesserungen: Formel beschriftet, Akronym deutlicher

\subsection{Technical Details}
    The generation of the Graphs and the Monte Carlo Simulation are implemented
    in C, all needed random numbers are generated by the GSL \cite{GSL}
    implementation of \emph{Mersenne Twister} \cite{Matsumoto1998} and
    the generated data is evaluated via Python scripts.
    The entire source code is available at \url{https://github.com/surt91/IsingFerromagnet}.\\
    Most simulations were carried out on HERO, the \emph{H}igh-\emph{E}nd
    Computing \emph{R}esource \emph{O}ldenburg.\\

>>>>

\subsection{Technical Details}
    The generation of the Graphs and the Monte Carlo Simulation are implemented
    in C, all needed random numbers are generated by the GSL \cite{GSL}
    implementation of \emph{Mersenne Twister} \cite{Matsumoto1998} and
    the generated data is evaluated via Python scripts.
    Most simulations were carried out on HERO, the \textbf{H}igh-\textbf{E}nd
    Computing \textbf{R}esource \textbf{O}ldenburg.
    The entire source code is available at \url{https://github.com/surt91/IsingFerromagnet}.\\
